R Markdown for Reproducible Research

### 2019-01-07 paper.Rmd
make progress on workflow section

This process is tedious and error prone: 
 - moving the results to another medium
 - copying values, data, plots, images, etc.
 - injecting values into prose

@@

@@

>>>>

This process is tedious and error prone: 
 - moving the results to another medium (from script output to a PowerPoint)
 - copying values, data, plots, images, etc.
 - injecting values into prose (i.e. There are 45 rows in this dataset)

@@

This problem and solution can be reduced to a paradigm of _best practices_ in
which reproducible, data-driven research is greatly simplified by R Markdown.
There are many [much more thorough](todo) articles on the topic, but we will
hit the highlights.

- Define input datasets, resources, or other dependencies
- Manage R packages in a [reproducible fashion](todo)
- Write narrative and code together into an R Markdown document
- Ensure that the narrative is programmatically dependent on the data
- Configure settings so that the R Markdown document produces final output

## AN EXAMPLE

@@

## INCLUDING PYTHON

## CUSTOMIZED EMAILS
